\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

\begin{flushleft}
\textbf{Sai Manoj Kartala} \\
Albany, NY 12203 \\
kartalasaimanoj@gmail.com \\
+1-518-941-0211 \\
\href{https://www.linkedin.com/in/saimanojkartala}{LinkedIn} | Portfolio
\end{flushleft}

\vspace{0.2in}

\today

\vspace{0.15in}

\begin{flushleft}
ITS Human Resources \\
Office of Information Technology Services \\
Empire State Plaza, Swan Street Building, Core 4, Floor 1 \\
Albany, NY 12220
\end{flushleft}

\vspace{0.15in}

\textbf{Re: Business Systems Analyst 1 (NY HELPS) - 10066 - Vacancy ID: 201565}

\vspace{0.15in}

Dear Hiring Manager,

I am writing to express my strong interest in the Business Systems Analyst 1 (NY HELPS) position (Vacancy ID: 201565) at the New York State Office of Information Technology Services. With a Master of Science in Computer Science from SUNY Albany, extensive experience in business analysis, requirements elicitation, and a proven track record of identifying solutions that improve system efficiency and effectiveness, I am well-qualified to provide analysis and design support for multiple agencies' and shared service teams.

\textbf{Requirements Elicitation and Business Analysis:} As Entrepreneurial Lead in the NSF I-Corps program, I conducted 30+ customer discovery interviews to elicit requirements and validate product–market fit for AI/AR STEM platforms, demonstrating my ability to elicit requirements as the foundation for solutions to organizational business needs. I mapped competitive landscapes, defined go-to-market strategies, and delivered commercialization plans, showcasing my capability to gather comprehensive business requirements and translate them into actionable solutions. At Venture Starters, I analyzed sector data across AI, HealthTech, FinTech, and SaaS, uncovering \$2M+ in potential opportunities, demonstrating my ability to perform business systems analysis and identify improvement opportunities.

\textbf{Solution Identification and Process Improvement:} Throughout my career, I have identified solutions aimed at improving the efficiency and effectiveness of systems, business processes, and products. I automated grading processes using Python scripts, reducing evaluation time by 20\%, and built automated BI dashboards that accelerated reporting by 25\%, demonstrating my ability to identify and implement solutions that enhance business processes. At MARVLS, LLC, I optimized system efficiency, reducing scene load times by 40\%, showcasing my capability to analyze systems and recommend improvements that fulfill business requirements.

\textbf{Documentation and Requirements Specification:} I have extensive experience describing in written documents what systems, processes, or products must do to satisfy established business requirements. Throughout my projects, I have created comprehensive documentation for system requirements, technical specifications, and business processes. I developed detailed documentation for AI-powered platforms, data pipelines, and system architectures, ensuring clear communication of requirements and system functionality. My experience includes documenting workflow processes, data inputs and outputs, and overall program goals and objectives.

\textbf{SDLC and Requirements Validation:} Throughout my career, I have contributed to all phases of the system development life cycle, from requirements gathering to design, development, testing, and maintenance. I have validated requirements throughout the SDLC by working closely with stakeholders, conducting reviews, and ensuring solutions meet business needs. My experience includes participating in requirements validation sessions, gathering feedback, and refining requirements based on stakeholder input, ensuring alignment between business needs and technical solutions.

\textbf{Test Planning and Scenario Development:} I have extensive experience developing test plans and scenarios, testing scenarios, and reviewing test results. As a Graduate Student Assistant, I review and grade 50+ coding assignments weekly, performing code reviews and identifying issues, which demonstrates my ability to develop test scenarios and validate system functionality. I have experience with functional testing, system testing, and regression testing, and have identified constraints and risks in system implementations. My work includes testing full-stack applications and ensuring they meet business requirements.

\textbf{Stakeholder Communication:} I have extensive experience communicating with stakeholders throughout the development process. My role conducting customer discovery interviews and presenting to mentors and investors demonstrates my ability to communicate effectively with agency management, users, vendors, consultants, and IT staff. I have participated in meetings to discuss solution options and recommend appropriate solutions for meeting program requirements, which is essential for this position.

\textbf{Cost/Benefit Analysis and Technical Feasibility:} My experience includes gathering, organizing, and performing preliminary analysis of information about costs, benefits, advantages, disadvantages, and technical feasibility. At Venture Starters, I analyzed sector data and evaluated opportunities, demonstrating my ability to assess the feasibility and benefits of proposed solutions. I have experience analyzing the impact of implementing new or modified systems, as demonstrated in my work evaluating system enhancements and optimizations.

\textbf{Design Activities and Workflow Documentation:} I have experience with various design activities, including creating specifications and workflow diagrams. My work includes designing system architectures, creating technical specifications, and documenting business processes. I have experience creating workflow diagrams and process documentation, which is essential for documenting business systems and processes, including workflow processes, data input and output activities, and descriptions of data elements.

\textbf{Impact Analysis:} I have experience analyzing the impact of implementing new or modified systems on other programs and processes. My work includes evaluating system changes, assessing their impact on existing systems, and ensuring seamless integration. I have experience identifying dependencies and potential impacts of system modifications, which is essential for analyzing the impact of implementing new or modified systems on other agency programs.

\textbf{Financial Document Processing:} While I may not have direct experience processing the specific financial documents mentioned, I have experience with project management, change management, and documentation processes. My experience includes managing project requests, tracking changes, and maintaining documentation, which provides a foundation for processing financial documents such as project requests, product requests, and change requests.

I am particularly excited about this opportunity to contribute to business systems analysis for multiple agencies and shared service teams, ensuring that IT solutions effectively meet business needs and improve organizational efficiency. My current residence in Albany, NY, and commitment to New York State residency make me an ideal candidate. I am eager to leverage my business analysis experience and technical expertise to support ITS initiatives and help agencies achieve their program goals and objectives.

Thank you for considering my application. I have attached my resume for your review and look forward to the opportunity to discuss how my business analysis experience and technical expertise align with your team's needs.

\vspace{0.2in}

Sincerely, \\
\vspace{0.3in}
Sai Manoj Kartala

\end{document}


